Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Grammar
Update comment
"BDD includes TDD, amongst other software development metho..", again

BDD includes TDD, but with a terminology and mindset shifted towards
specification instead of testing. BDD also includes other software
development methods, such as automatic test discovery and continuous
integration~\cite{ci}.  In BDD, specifications can be used for
automatic testing.  BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

\begin{quote}
    \emph{kazu: I would like to exchange 2nd sentence and 3rd sentence:}

    sol: this paragraph still has issues
    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that thing
            e.g. work with CI.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but we only focus on TDD.  I think
            meaning got lost now.
    \end{itemize}

>>>>

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automatic testing.  BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

\begin{quote}
    BDD also includes other software development methods, such as
    automatic test discovery and continuous integration~\cite{ci}.

    sol: I removed this, and reverted the paragraph to it's previous
    version, because I think there were several issues.

    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that
            \emph{testing is more fun} and \emph{things e.g. work with
            CI}.  This are two things, but both justify automation.
            We only need this to justify our discussion of Cabal
            integration and automatic test discovery.  If we remove
            those, we do not state that ``automation is an important
            aspect of BDD''.  This may be a solution.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but that we do not cover them.  This
            is very important.  And I think meaning got lost with the
            change, hence the revert.
    \end{itemize}
